Assessment of zonally symmetric and asymmetric components of the Southern Annular Mode using a novel approach

### 2021-05-04 analysis/paper/asymsam.Rmd
Agrega comentario de que 50 hPa no está centrado
#18

geom_coords <- function() {
  list(
    geom_segment(data = data.frame(xstart =  seq(0, 360-30, by = 30), 
                                   xend =  seq(0, 360-30, by = 30),
                                   ystart = -90+15,
                                   yend = Inf),
                 aes(x = xstart, xend = xend, y = ystart, yend = yend),
                 size = 0.1, alpha = 0.5),

    # geom_vline(xintercept = seq(0, 360-30, by = 30), size = 0.1, alpha = 0.5),

      geom_hline(yintercept = seq(-90, 0, by = 15), size = 0.1, alpha = 0.5),
      shadowtext::geom_shadowtext(data = data.frame(x = 0, y = seq(-90 + 15, 0, by = 15)),
                                  aes(x, y, label = LatLabel(y)), size = 2, alpha = 0.5,
                                  colour = "black",
                                  bg.colour = "white" ) 
  )
}

@@

In the stratosphere, the spatial pattern associated with the SAM is clearly dominated by a zonally symmetric, monopolar structure (Figure \@ref(fig:2d-regr)a.1) which is not centred in the South Pole.
On the other hand, the monopole associated with S\nobreakdash-SAM (Figure \@ref(fig:2d-regr)c.1) is more symmetric.
Furthermore, the regression pattern of A\nobreakdash-SAM is characterized by a wave-1 structure with centres over the Drake Passage in the Western Hemisphere and Davis Sea in the Eastern Hemisphere

>>>>

geom_coords <- function() {
  list(
    geom_segment(data = data.frame(xstart =  seq(0, 360 - 30, by = 30), 
                                   xend =  seq(0, 360 - 30, by = 30),
                                   ystart = -90 + 15,
                                   yend = Inf),
                 aes(x = xstart, xend = xend, y = ystart, yend = yend),
                 size = 0.1, alpha = 0.5),

      geom_hline(yintercept = seq(-90, 0, by = 15), size = 0.1, alpha = 0.5),
      shadowtext::geom_shadowtext(data = data.frame(x = 0, y = seq(-90 + 15, 0, by = 15)),
                                  aes(x, y, label = LatLabel(y)), size = 1.5, alpha = 0.5,
                                  colour = "black",
                                  bg.colour = "white" ) 
  )
}

@@

In the stratosphere, the spatial pattern associated with the SAM is clearly dominated by a zonally symmetric, monopolar structure (Figure \@ref(fig:2d-regr)a.1) which is not centred in the South Pole.
On the other hand, the monopole associated with S\nobreakdash-SAM (Figure \@ref(fig:2d-regr)c.1) is more symmetric, although still is not perfectly centred in the South Pole. 
Furthermore, the regression pattern of A\nobreakdash-SAM is characterized by a wave-1 structure with centres over the Drake Passage in the Western Hemisphere and Davis Sea in the Eastern Hemisphere
